{\LARGE Basis Choice for Scalar-on-Function Regression \\ with Applications to Near-Infrared Spectroscopy}

### 2022-02-06 Paper/main.tex
Limit to the number of Eigenfunctions added

	 \begin{equation}\label{DGP1}
	 	Y(\omega) = \alpha + \int_{0}^{1}{X(\omega)(s)\beta(s) \mathrm{d}s} + \epsilon(\omega),
	 	\qquad i = 1, ..., n
	 \end{equation}

@@

	\begin{equation}\label{Fourier_Series}
		s(x) = \frac{A_0}{2} + \sum_{i = 1}^{\infty} A_n \cos(2\pi n x - \phi_n) = \frac{a_0}{2} + \sum_{i = 1}^{\infty}\left[a_n \cos(2\pi n x) + b_n \sin(2\pi n x)\right]
	\end{equation}

@@

	\begin{equation}
		\hat{\mu}(t) = \frac{1}{n}\sum_{i = 1}^{n}x_i(t)
	\end{equation}

	\begin{equation}
		\hat{c}(t,s) = \frac{1}{n} \sum_{i = 1}^{n} \left(x_i(t) - \hat{\mu}(t)\right) \left(x_i(s) - \hat{\mu}(s)\right)
	\end{equation}

	With these it is possible to derive a set of sample analogs $\{(\hat{\lambda}^m, \hat{\nu}^m) \: \vert \: m \in \mathcal{M}\}$ for $\{(\lambda^m, \nu^m) \: \vert \: m \in \mathbb{N}\}$ as the solutions of the following equation. {\color{red} I think the number of principal components has to be smaller then the number of observations. So I can give more information about $\mathcal{M}$.}

@@

	\begin{equation}
		x_i(t) = \hat{\mu}(t) + \sum_{j = 1}^{{\color{red} !!!}} \hat{\xi}_{i}^{m} \hat{\nu}^{m}(t)
	\end{equation}
	where the $\hat{\xi}_{i}^m$ are derived as

@@

	\begin{equation}
		Y = \begin{pmatrix}
			y_1 \\ \vdots \\ y_n
		\end{pmatrix}, \quad
		Z = \begin{pmatrix}
			1 & \tilde{Z}_{1,1} & \dots & \tilde{Z}_{1,J} \\
			\vdots & \vdots & \ddots & \vdots \\
			1 & \tilde{Z}_{n,1} & \dots & \tilde{Z}_{n,J}
		\end{pmatrix}
	\end{equation}

@@

	\begin{equation}
		\begin{split}
			y_i &= \alpha + \int_{0}^{1} {\color{red}x_i(s)} \beta(s) \mathrm{d}s + \epsilon_i
			= \alpha + \int_{0}^{1} {\color{red}\left(\hat{\mu}(s) + \sum_{m \in \mathcal{M}} \hat{\xi}^m_i \hat{\nu}^m(s)\right)} \beta(s) \mathrm{d}s + \epsilon_i\\
			&= {\color{teal}\alpha + \int_{0}^{1} \hat{\mu}(s) \beta(s) \mathrm{d}s} + \sum_{m \in \mathcal{M}} \hat{\xi}^m_i {\color{violet}\int_{0}^{1} \hat{\nu}^m(s) \beta(s) \mathrm{d}s} + \epsilon_i
			= {\color{teal}\bar{\alpha}} + \sum_{m \in \mathcal{M}} \hat{\xi}^m_i {\color{violet}\hat{\beta}^m} + \epsilon_i
		\end{split}
	\end{equation}

@@

	\begin{equation}
		\begin{split}
			y_i &= \alpha + \int_{0}^{1} {\color{red}x_i(s)} {\color{blue}\beta(s)} \mathrm{d}s + \epsilon_i
			= \alpha + \int_{0}^{1} {\color{red}\left(\hat{\mu}(s) + \sum_{m \in \mathcal{M}} \hat{\xi}^{m}_i \hat{\nu}^{m}(s)\right)} {\color{blue}\left(\sum_{j \in \mathcal{I}} b_j \phi_j(s)\right)} \mathrm{d}s + \epsilon_i\\
			&= \alpha + \int_{0}^{1} \left[ \sum_{j \in \mathcal{I}} b_j \phi_j(s) \hat{\mu}(s) + \sum_{m \in \mathcal{M}} \left[ \hat{\xi}^m_i \sum_{j \in \mathcal{I}} b_j \hat{\nu}^m(s) \phi_j(s) \right] \right] \mathrm{d}s + \epsilon_i \\
			&= \alpha + \sum_{j \in \mathcal{I}} b_j \int_{0}^{1} \phi_j(s) \hat{\mu}(s) \mathrm{d}s + \sum_{m \in \mathcal{M}} \left[ \hat{\xi}^m_i \sum_{j \in \mathcal{I}} b_j \int_{0}^{1}\hat{\nu}^m(s) \phi_j(s) \mathrm{d}s \right] + \epsilon_i
		\end{split}
	\end{equation}

@@

	\begin{equation}\label{fpcr_reg_both_expansions}
		\begin{split}
			y_i &= \alpha + \int_{0}^{1} \left(\hat{\mu}(s) + \sum_{m \in \mathcal{M}} \hat{\xi}^{m}_i \hat{\nu}^{m}(s)\right) {\color{blue}\left(\sum_{j = 1}^{J} b_j \phi_j(s) + \delta_{\beta}^{J}(s)\right)} \mathrm{d}s + \epsilon_i\\
			&= \alpha + \sum_{j = 1}^{J} b_j \int_{0}^{1} \phi_j(s) \hat{\mu}(s) \mathrm{d}s + \int_{0}^{1} \delta_{\beta}^{J}(s) \hat{\mu}(s) \mathrm{d}s + \sum_{m \in \mathcal{M}} \left[ \hat{\xi}^m_i \sum_{j = 1}^{J} b_j \int_{0}^{1}\hat{\nu}^m(s) \phi_j(s) \mathrm{d}s \right] \\
			& \quad \quad + \sum_{m \in \mathcal{M}} \left[ \hat{\xi}^m_i \int_{0}^{1}\hat{\nu}^m(s) \delta_{\beta}^{J}(s) \mathrm{d}s \right] + \epsilon_i
		\end{split}
	\end{equation}

@@

	\begin{equation}
		\begin{split}
			y_i & = \tilde{\alpha}^L
			+ \sum_{m \in \mathcal{M}} \left[ \left(\tilde{\xi}^{m,L}_{i} + \delta_{\xi, i}^{m, L} \right) \sum_{j = 1}^{L} b_j \int_{0}^{1} \left(\tilde{\nu}^{m,L}(s) + \delta_{\nu, m}^L(s) \right) \phi_j(s) \mathrm{d}s \right] 
			+ \epsilon_i \\
			& = \tilde{\alpha}^L
			+ \sum_{m \in \mathcal{M}} \left[ \tilde{\xi}^{m,L}_{i} \sum_{j = 1}^{L} b_j \int_{0}^{1} \tilde{\nu}^{m,L}(s) \phi_j(s) \mathrm{d}s \right] 
			+ \sum_{m \in \mathcal{M}} \left[ \tilde{\xi}^{m,L}_{i} \sum_{j = 1}^{L} b_j \int_{0}^{1} \delta_{\nu, m}^L(s) \phi_j(s) \mathrm{d}s \right] \\
			& \quad \quad + \sum_{m \in \mathcal{M}} \left[ \delta_{\xi, i}^{m, L} \sum_{j = 1}^{L} b_j \int_{0}^{1} \tilde{\nu}^{m,L}(s) \phi_j(s) \mathrm{d}s \right] 
			+ \sum_{m \in \mathcal{M}} \left[ \delta_{\xi, i}^{m, L} \sum_{j = 1}^{L} b_j \int_{0}^{1} \delta_{\nu, m}^L(s) \phi_j(s) \mathrm{d}s \right]
			+ \epsilon_i \\
			& \approx \tilde{\alpha}^L
			+ \sum_{m \in \mathcal{M}} \left[ \tilde{\xi}^{m,L}_{i} \sum_{j = 1}^{L} b_j \int_{0}^{1} \tilde{\nu}^{m,L}(s) \phi_j(s) \mathrm{d}s \right] + \epsilon_i
		\end{split}
	\end{equation}

@@

	\begin{equation}
		Y = \begin{pmatrix}
			y_1 \\ \vdots \\ y_n
		\end{pmatrix}, \quad
		Z = \begin{pmatrix}
			1 & \tilde{\xi}^{1,L}_{1} & \dots & \tilde{\xi}^{M,L}_{1} \\
			\vdots & \vdots & \ddots & \vdots \\
			1 & \tilde{\xi}^{1,L}_{n} & \dots & \tilde{\xi}^{M,L}_{n}
		\end{pmatrix}
	\end{equation}

@@

	\section{Proofs}
	\subsection{Lemma} \label{Proof1}
	The curves $X(t) \in \mathbb{L}^2[0,1]$ is expanded by the eigenfunctions $\{\nu^m\}$ as (\ref{KarhunenLoeve}). The coefficients $\xi^{m}$ of basis functions satisfy the following properties:
	\begin{enumerate}
		\item $\mathbb{E}\left[\xi^m(\omega)\right] = 0$
		\item $Cov\left(\xi^m(\omega), \xi^n(\omega)\right) = \delta^{m,n}\lambda^m$% if $m \neq n$
		\item $Var\left(\xi^m(\omega)\right) = \lambda^m$
	\end{enumerate}
	Remind that $\delta^{m,n} = 0$ if $m \neq n$, otherwise 1.
	\begin{proof}
		Assume that $F(t)$ is the centered process of $X(t)$, namely, $F(t) = X(t) - \int_{\Omega}X(t)dP(\omega)$. To obtain the first result, we can show that
		\begin{equation}\label{Lemma1}
			\begin{split}
				\mathbb{E}[\xi^m] = & \mathbb{E} \biggl\lbrack \int_{0}^{1} F(t) \nu_{j}(t)dt\biggr\rbrack\\
				= & \int_{\Omega} \int_{0}^{1} F(t) \nu^m(t) dt dP(\omega)\\
				= & \int_{0}^{1} \int_{\Omega} F(t) \nu^m(t) dP(\omega) dt \quad \text{(Fubini)}\\
				= & \int_{0}^{1} {\color{red}\int_{\Omega} F(t) dP(\omega)} \nu^m(t) dt\\
				= & \int_{0}^{1} {\color{red}\mathbb{E}[F(t)]} \nu^m(t) dt = 0
			\end{split}
		\end{equation}
		where $\mathbb{E}[F(t)]$ is 0 since $F(t)$ is a centered process.
		The second claim is proved as:
		\begin{equation}\label{Lemma2}
			\begin{split}
				\mathbb{E} [\xi^m \xi^n] = & \mathbb{E}  \biggl\lbrack \int_{0}^{1} F(s) \nu^m(s)ds \int_{0}^{1} F(t) \nu^n(t)dt  \biggr\rbrack\\
				= & \mathbb{E} \biggl\lbrack {\int_{0}^{1} \int_{0}^{1} F(s) \nu^m(s) F(t) \nu^n(t) ds dt} \biggr\rbrack \quad \text{(Fubini)}\\
				= & \int_{0}^{1} {\color{red}\int_{0}^{1} \mathbb{E}[{F(s)F(t)}] \nu^m(s)} \nu^n(t) {\color{red}ds} dt\\
				= & \int_{0}^{1} {\color{red}\left(\int_{0}^{1}c(s,t)\nu^m(s)ds \right)} \nu^n(t) dt \\
				= & \int_{0}^{1}{\color{red}[K\nu^m](t)}\nu^n(t)dt\\
				= & \langle K \nu^m, \nu^n \rangle\\
				= & \langle \lambda^m \nu^m, \nu^n \rangle = \delta^{m,n}\lambda^{m}
			\end{split}
		\end{equation}
		where $\delta^{m,n} = 1$ if $m = n$, otherwise 0. The result is produced from orthonormaility of the eigenfunctions.
		\begin{equation}
			Cov\left(\xi^m, \xi^n\right) = \mathbb{E}[\xi^m \xi^n] - \mathbb{E}[\xi^m]\mathbb{E}[\xi^n] = \delta^{m,n}\lambda^{m}
		\end{equation}
		where $\mathbb{E}[\xi^m] = \mathbb{E}[\xi^n] = 0$ as the first property.
		The last assertion is confirmed from the above two properties.
		\begin{equation}\label{Lemma3}
			Var[\xi^m] = \mathbb{E}\left[(\xi^m - \mathbb{E}[\xi^m])^{2}\right] = \mathbb{E}[(\xi^m)^{2}] =\lambda^m
		\end{equation}
		The original process also has the same properties as the centered one since
		\begin{equation}
			X(t) = F(t) + \mathbb{E}[X(t)] = \mu(t) + \sum_{m=1}^{\infty}\xi^m\nu^m(t)
		\end{equation}
	\end{proof}

>>>>

	 \begin{equation}\label{DGP1}
	 	Y(\omega) = \alpha + \int_{0}^{1}{X(\omega)(s)\beta(s) \mathrm{d}s} + \epsilon(\omega),
	 	\qquad i = 1, ..., N
	 \end{equation}

@@

	\begin{equation}\label{Fourier_Series}
		s(x) = \frac{A_0}{2} + \sum_{i = 1}^{\infty} A_n \cos(2\pi i x - \phi_n) = \frac{a_0}{2} + \sum_{i = 1}^{\infty}\left[a_i \cos(2\pi i x) + b_i \sin(2\pi i x)\right]
	\end{equation}

@@

	\begin{equation}
		\hat{\mu}(t) = \frac{1}{N}\sum_{i = 1}^{N}x_i(t)
	\end{equation}

	\begin{equation}
		\hat{c}(t,s) = \frac{1}{N} \sum_{i = 1}^{N} \left(x_i(t) - \hat{\mu}(t)\right) \left(x_i(s) - \hat{\mu}(s)\right)
	\end{equation}

	With these it is possible to derive a set of sample analogs $\{(\hat{\lambda}^m, \hat{\nu}^m) \: \vert \: m = 1, \dots, N-1\}$ for $\{(\lambda^m, \nu^m) \: \vert \: m \in \mathbb{N}\}$ as the solutions of the following equation. As in the case of ordinary principal components, the number of eigenfunctions corresponding to non-zero eigenvalues is limited (cf. chapter 8.2.3 \cite{ramsay_functional_2005}). As each curve is infinite dimensional, there is no upper limit to this number due to the dimensionality. However the number of curves still imposes an upper limit of $N-1$ non-zero eigenvalues, where $N$ is the number of curves in the data set.

@@

	\begin{equation}
		x_i(t) = \hat{\mu}(t) + \sum_{j = 1}^{N-1} \hat{\xi}_{i}^{m} \hat{\nu}^{m}(t)
	\end{equation}
	where the $\hat{\xi}_{i}^m$ are derived as

@@

	\begin{equation}
		Y = \begin{pmatrix}
			y_1 \\ \vdots \\ y_n
		\end{pmatrix}, \quad
		Z = \begin{pmatrix}
			1 & \tilde{Z}_{1,1} & \dots & \tilde{Z}_{1,J} \\
			\vdots & \vdots & \ddots & \vdots \\
			1 & \tilde{Z}_{N,1} & \dots & \tilde{Z}_{N,J}
		\end{pmatrix}
	\end{equation}

@@

	\begin{equation}
		\begin{split}
			y_i &= \alpha + \int_{0}^{1} {\color{red}x_i(s)} \beta(s) \mathrm{d}s + \epsilon_i
			= \alpha + \int_{0}^{1} {\color{red}\left(\hat{\mu}(s) + \sum_{m = 1}^{N-1} \hat{\xi}^m_i \hat{\nu}^m(s)\right)} \beta(s) \mathrm{d}s + \epsilon_i\\
			&= {\color{teal}\alpha + \int_{0}^{1} \hat{\mu}(s) \beta(s) \mathrm{d}s} + \sum_{m = 1}^{N-1} \hat{\xi}^m_i {\color{violet}\int_{0}^{1} \hat{\nu}^m(s) \beta(s) \mathrm{d}s} + \epsilon_i
			= {\color{teal}\bar{\alpha}} + \sum_{m = 1}^{N-1} \hat{\xi}^m_i {\color{violet}\hat{\beta}^m} + \epsilon_i
		\end{split}
	\end{equation}

@@

	\begin{equation}
		\begin{split}
			y_i &= \alpha + \int_{0}^{1} {\color{red}x_i(s)} {\color{blue}\beta(s)} \mathrm{d}s + \epsilon_i
			= \alpha + \int_{0}^{1} {\color{red}\left(\hat{\mu}(s) + \sum_{m = 1}^{N-1} \hat{\xi}^{m}_i \hat{\nu}^{m}(s)\right)} {\color{blue}\left(\sum_{j \in \mathcal{I}} b_j \phi_j(s)\right)} \mathrm{d}s + \epsilon_i\\
			&= \alpha + \int_{0}^{1} \left[ \sum_{j \in \mathcal{I}} b_j \phi_j(s) \hat{\mu}(s) + \sum_{m = 1}^{N-1} \left[ \hat{\xi}^m_i \sum_{j \in \mathcal{I}} b_j \hat{\nu}^m(s) \phi_j(s) \right] \right] \mathrm{d}s + \epsilon_i \\
			&= \alpha + \sum_{j \in \mathcal{I}} b_j \int_{0}^{1} \phi_j(s) \hat{\mu}(s) \mathrm{d}s + \sum_{m = 1}^{N-1} \left[ \hat{\xi}^m_i \sum_{j \in \mathcal{I}} b_j \int_{0}^{1}\hat{\nu}^m(s) \phi_j(s) \mathrm{d}s \right] + \epsilon_i
		\end{split}
	\end{equation}

@@

	\begin{equation}\label{fpcr_reg_both_expansions}
		\begin{split}
			y_i &= \alpha + \int_{0}^{1} \left(\hat{\mu}(s) + \sum_{m = 1}^{N-1} \hat{\xi}^{m}_i \hat{\nu}^{m}(s)\right) {\color{blue}\left(\sum_{j = 1}^{J} b_j \phi_j(s) + \delta_{\beta}^{J}(s)\right)} \mathrm{d}s + \epsilon_i\\
			&= \alpha + \sum_{j = 1}^{J} b_j \int_{0}^{1} \phi_j(s) \hat{\mu}(s) \mathrm{d}s + \int_{0}^{1} \delta_{\beta}^{J}(s) \hat{\mu}(s) \mathrm{d}s + \sum_{m = 1}^{N-1} \left[ \hat{\xi}^m_i \sum_{j = 1}^{J} b_j \int_{0}^{1}\hat{\nu}^m(s) \phi_j(s) \mathrm{d}s \right] \\
			& \quad \quad + \sum_{m = 1}^{N-1} \left[ \hat{\xi}^m_i \int_{0}^{1}\hat{\nu}^m(s) \delta_{\beta}^{J}(s) \mathrm{d}s \right] + \epsilon_i
		\end{split}
	\end{equation}

@@

	\begin{equation}
		\begin{split}
			y_i & = \tilde{\alpha}^L
			+ \sum_{m = 1}^{N-1} \left[ \left(\tilde{\xi}^{m,L}_{i} + \delta_{\xi, i}^{m, L} \right) \sum_{j = 1}^{L} b_j \int_{0}^{1} \left(\tilde{\nu}^{m,L}(s) + \delta_{\nu, m}^L(s) \right) \phi_j(s) \mathrm{d}s \right] 
			+ \epsilon_i \\
			& = \tilde{\alpha}^L
			+ \sum_{m = 1}^{N-1} \left[ \tilde{\xi}^{m,L}_{i} \sum_{j = 1}^{L} b_j \int_{0}^{1} \tilde{\nu}^{m,L}(s) \phi_j(s) \mathrm{d}s \right] 
			+ \sum_{m = 1}^{N-1} \left[ \tilde{\xi}^{m,L}_{i} \sum_{j = 1}^{L} b_j \int_{0}^{1} \delta_{\nu, m}^L(s) \phi_j(s) \mathrm{d}s \right] \\
			& \quad \quad + \sum_{m = 1}^{N-1} \left[ \delta_{\xi, i}^{m, L} \sum_{j = 1}^{L} b_j \int_{0}^{1} \tilde{\nu}^{m,L}(s) \phi_j(s) \mathrm{d}s \right] 
			+ \sum_{m = 1}^{N-1} \left[ \delta_{\xi, i}^{m, L} \sum_{j = 1}^{L} b_j \int_{0}^{1} \delta_{\nu, m}^L(s) \phi_j(s) \mathrm{d}s \right]
			+ \epsilon_i \\
			& \approx \tilde{\alpha}^L
			+ \sum_{m = 1}^{N-1} \left[ \tilde{\xi}^{m,L}_{i} \sum_{j = 1}^{L} b_j \int_{0}^{1} \tilde{\nu}^{m,L}(s) \phi_j(s) \mathrm{d}s \right] + \epsilon_i
		\end{split}
	\end{equation}

@@

	\begin{equation}
		Y = \begin{pmatrix}
			y_1 \\ \vdots \\ y_n
		\end{pmatrix}, \quad
		Z = \begin{pmatrix}
			1 & \tilde{\xi}^{1,L}_{1} & \dots & \tilde{\xi}^{M,L}_{1} \\
			\vdots & \vdots & \ddots & \vdots \\
			1 & \tilde{\xi}^{1,L}_{N} & \dots & \tilde{\xi}^{M,L}_{N}
		\end{pmatrix}
	\end{equation}

@@

	\section{Proofs}
	\subsection{Lemma} \label{Proof1}
	The curves $X(t) \in \mathbb{L}^2[0,1]$ is expanded by the eigenfunctions $\{\nu^m\}$ as (\ref{KarhunenLoeve}). The coefficients $\xi^{m}$ of basis functions satisfy the following properties:
	\begin{enumerate}
		\item $\mathbb{E}\left[\xi^m(\omega)\right] = 0$
		\item $Cov\left(\xi^m(\omega), \xi^n(\omega)\right) = \delta^{m,n}\lambda^m$% if $m \neq n$
		\item $Var\left(\xi^m(\omega)\right) = \lambda^m$
	\end{enumerate}
	Remind that $\delta^{m,n} = 0$ if $m \neq n$, otherwise 1.
	\begin{proof}
		Assume that $F(t)$ is the centered process of $X(t)$, namely, $F(t) = X(t) - \int_{\Omega}X(t)dP(\omega)$. To obtain the first result, we can show that
		\begin{equation}\label{Lemma1}
			\begin{split}
				\mathbb{E}[\xi^m] = & \mathbb{E} \biggl\lbrack \int_{0}^{1} F(t) \nu_{j}(t)dt\biggr\rbrack\\
				= & \int_{\Omega} \int_{0}^{1} F(t) \nu^m(t) dt dP(\omega)\\
				= & \int_{0}^{1} \int_{\Omega} F(t) \nu^m(t) dP(\omega) dt \quad \text{(Fubini)}\\
				= & \int_{0}^{1} {\color{red}\int_{\Omega} F(t) dP(\omega)} \nu^m(t) dt\\
				= & \int_{0}^{1} {\color{red}\mathbb{E}[F(t)]} \nu^m(t) dt = 0
			\end{split}
		\end{equation}
		where $\mathbb{E}[F(t)]$ is 0 since $F(t)$ is a centered process.
		The second claim is proved as:
		\begin{equation}\label{Lemma2}
			\begin{split}
				\mathbb{E} [\xi^m \xi^n] = & \mathbb{E}  \biggl\lbrack \int_{0}^{1} F(s) \nu^m(s)ds \int_{0}^{1} F(t) \nu^n(t)dt  \biggr\rbrack\\
				= & \mathbb{E} \biggl\lbrack {\int_{0}^{1} \int_{0}^{1} F(s) \nu^m(s) F(t) \nu^n(t) ds dt} \biggr\rbrack \quad \text{(Fubini)}\\
				= & \int_{0}^{1} {\color{red}\int_{0}^{1} \mathbb{E}[{F(s)F(t)}] \nu^m(s)} \nu^n(t) {\color{red}ds} dt\\
				= & \int_{0}^{1} {\color{red}\left(\int_{0}^{1}c(s,t)\nu^m(s)ds \right)} \nu^n(t) dt \\
				= & \int_{0}^{1}{\color{red}[K\nu^m](t)}\nu^n(t)dt\\
				= & \langle K \nu^m, \nu^n \rangle\\
				= & \langle \lambda^m \nu^m, \nu^n \rangle = \delta^{m,n}\lambda^{m}
			\end{split}
		\end{equation}
		where $\delta^{m,n} = 1$ if $m = n$, otherwise 0. The result is produced from orthonormality of the eigenfunctions.
		\begin{equation}
			Cov\left(\xi^m, \xi^n\right) = \mathbb{E}[\xi^m \xi^n] - \mathbb{E}[\xi^m]\mathbb{E}[\xi^n] = \delta^{m,n}\lambda^{m}
		\end{equation}
		where $\mathbb{E}[\xi^m] = \mathbb{E}[\xi^n] = 0$ as the first property.
		The last assertion is confirmed from the above two properties.
		\begin{equation}\label{Lemma3}
			Var[\xi^m] = \mathbb{E}\left[(\xi^m - \mathbb{E}[\xi^m])^{2}\right] = \mathbb{E}[(\xi^m)^{2}] =\lambda^m
		\end{equation}
		The original process also has the same properties as the centered one since
		\begin{equation}
			X(t) = F(t) + \mathbb{E}[X(t)] = \mu(t) + \sum_{m=1}^{\infty}\xi^m\nu^m(t)
		\end{equation}
	\end{proof}
